Safety and Liveness of Unmanned Aerial Vehicle Platoons on Air Highways

### 2016-05-14 docs/AIAA 2016 highway platooning/conclusions.tex
Minor changes

% !TEX root = main.tex
\section{Conclusions}
To address the important and urgent problem of the traffic management of UAVs, we proposed to have platoons of UAVs traveling on air highways. We showed how such an airspace structure leads to a much easier safety and liveness analysis. We provided simulations which show that by organizing vehicles into platoons, many complex maneuvers can be performed using just a few different reachable sets.

For the placement of air highways over a region, we present the very intuitive and efficient fast marching algorithm for solving the Eikonal equation. Our algorithm allows us to take as input any arbitrary cost map representing the desirability of flying over any position in space, and produce a set of paths from any destination to a particular origin. Simple heurstic clustering methods can then be used to convert the sets of paths into a set of air highways.

>>>>

% !TEX root = main.tex
\section{Conclusions}
To address the important and urgent problem of the traffic management of UAVs, we proposed to have platoons of UAVs traveling on air highways. We showed how such an airspace structure leads to much easier safety and liveness analysis. We provided simulations which show that by organizing vehicles into platoons, many complex maneuvers can be performed using just a few different reachable sets.

For the placement of air highways over a region, we utilize the very intuitive and efficient fast marching algorithm for solving the Eikonal equation. Our algorithm allows us to take as input any arbitrary cost map representing the desirability of flying over any position in space, and produce a set of paths from any destination to a particular origin. Simple heuristic clustering methods can then be used to convert the sets of paths into a set of air highways.
